\sysfull

### 2018-08-04 paper/asplos19/intro.tex
changes to the intro (Przemek) conflict from Carlo resolved

%
\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figures/intro-figure-vert.pdf}
    \caption{\note{All this white padding is ugly} Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{C} in the figure). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{figure}
%
%\textbf{Task Decomposition of Intermittent Programs.}

\noindent\textbf{Crucial Drawback of Static Task Decomposition.} 
\note{Why no indent?}
Task-based programming and execution models require a
programmer~\cite{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to
statically decompose a program into a collection of tasks.  A \emph{task}, a top level function, can
include arbitrary computation that should be executed despite arbitrarily-timed power failures.
The programmer (or a compiler) explicitly expresses task-to-task control flow.
Fig.~\ref{fig:coalesce} illustrates how a program's tasks execute and
shows how task transitions can impose a run-time overhead. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at run-time.
%
A programmer may thus create very large tasks in an attempt to reduce task transitions
overhead. However, a very large task may require more energy to complete than a device's fixed hardware energy
buffer can hold which may lead to a task \emph{non-termination} problem. To eliminate this risk,
existing systems require the programmer to decompose a program into relatively small tasks to preserve execution progress. These constraints on task sizing leave an unsatisfying dilemma: large, efficient tasks that risk non-termination, or small tasks that are guaranteed to complete, but incur a high task transition and commit overhead. In this work,
we propose a third way, using a novel technique called \emph{adaptive task size execution by task coalescing/splitting} that efficiently executes small tasks, trimming unnecessary overheads, while avoiding the risk of non-termination.
%

>>>>

%
\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figures/intro-figure-vert.pdf}
    \caption{\note{All this white padding is ugly} Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{C}) of individual tasks (denoted as \texttt{T(x)}). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{figure}
%
%\textbf{Task Decomposition of Intermittent Programs.}

\noindent\textbf{Crucial Drawback of Static Task Decomposition.} 
\note{Why no indent?}
Task-based programming and execution models require a
programmer~\cite{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to
statically decompose a program into a collection of tasks. A \emph{task}, a top level function, can
include arbitrary computation that should be executed despite arbitrarily-timed power failures.
The programmer (or a compiler) explicitly expresses task-to-task control flow.
Fig.~\ref{fig:coalesce} illustrates how a program's tasks execute and shows how tasks transitions can impose a runtime overhead. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at runtime.
%
A programmer may thus create very large tasks in an attempt to reduce task transitions
overhead. However, a very large task may require more energy to complete than a device's fixed hardware energy
buffer can hold which may lead to a task \emph{non-termination} problem. To eliminate this risk,
existing systems require the programmer to decompose a program into relatively small tasks to preserve execution progress. These constraints on task sizing lead to the following dilemma: should large tasks be used, that are efficient but risk non-termination, or small tasks that are guaranteed to complete, but incur a high task transition and commit overhead. In this work,
we propose a third way, using a novel technique called \emph{adaptive task size execution by task coalescing/splitting} that efficiently executes small tasks, trimming unnecessary overheads, while avoiding the risk of non-termination.
